An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-04-12 tex/paper.tex
Update my name and affiliation

\documentclass{jors}

%% Set the header information

% Commenting out as this overrides the section titles.
%\pagestyle{fancy}
%\definecolor{mygray}{gray}{0.6}
%\renewcommand\headrule{}
%\rhead{\footnotesize 3}
%\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

% Nicer bibliography management
\usepackage[backend=biber, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

\usepackage{amsmath}  % Basic
\usepackage{booktabs}  % Better tables
\usepackage{graphicx}  % Images
\usepackage{hyperref}  % Links etc
\usepackage{minted}  % Code
\usepackage{multicol}  % Multi column list
\usepackage{subcaption}  % Subfigures

\begin{document}
%% Set the header information
\pagestyle{fancy}
\definecolor{mygray}{gray}{0.6}
\renewcommand\headrule{}
\rhead{\footnotesize 3}
\rhead{\textcolor{gray}{UP JORS software Latex paper template version 0.1}}

\rule{\textwidth}{1pt}

\section*{(1) Overview}\label{sec:sec:overview}

\vspace{0.5cm}

\section*{Title}

An open reproducible framework for the study of the iterated prisoner's
dilemma.

\section*{Authors}

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
        % Core devs (alphabetic order of last name after Vince as corresponding
        % goes first).
        \item Knight, Vincent
        \item Campbell, Owen
        \item Harper, Marc
        \item Langner, Karol
        % All devs (alphabetic order of last name)
        \item Campbell, James
        \item Campbell, Thomas
        \item Carney, Alex
        \item Chorley, Martin
        \item Davidson-Pilon, Cameron
        \item Glass, Kristian
        \item Ehrlich Tom{\'a}{\v s}
        \item Jones, Martin
        \item Koutsovoulos, Georgios
        \item Tibble, Holly
        \item M{\"u}ller, Jochen
        \item Palmer, Geraint
        \item Slavin, Paul
        \item Standen, Timothy
        \item Visintini, Luis
        \item Molden, Karl
    \end{enumerate}
\end{multicols}

\section*{Paper Author Roles and Affiliations}

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Cardiff University
\item Development; St. Nicholas Catholic High School, Hartford
\item Development; Cardiff University
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Edinburgh
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; Not affiliated
\item Development; The University of Manchester
\item Development; Cardiff University
\item Development; Not affiliated
\item Development; Not affiliated
    \end{enumerate}
\end{multicols}

\section*{Abstract}

The Axelrod library is an open source Python package that allows for
reproducible game theoretic research into the Iterated Prisoner's Dilemma.
This area of research began in the 1980s but suffers from a lack of
documentation and test code. The goal of the library is to provide such
a resource, with facilities for the design of new strategies and
interactions between them, as well as conducting tournaments and ecological
simulations for populations of strategies.

With a growing collection of 122 strategies, the library is a also a
platform for an original tournament that, in itself, is of interest to the
game theoretic community.

This paper describes the Iterated Prisoner's Dilemma, the Axelrod library
and its development, and insights gained from some novel research.

\section*{Keywords}

Game Theory; Prisoners Dilemma; Python

\section*{Introduction}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item To enable the reproduction of Iterated Prisoner's Dilemma
    research as easily as possible
    \item To produce the de-facto tool for any future Iterated Prisoner's
    Dilemma research
    \item To provide as simple a means as possible for anyone to define and
    contribute new and original Iterated Prisoner's Dilemma strategies
\end{itemize}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Open: all code is released under an MIT license;
    \item Reproducible and well-tested: at the time of writing there is an excellent level of
        integrated tests with 99.37\% coverage (including property based tests:
        \cite{Hypothesis3.0.3}
    \item Well-documented: all features of the library are documented for ease of
        use and modification
    \item Extensive: 123 strategies are included, with infinitely-many
        strategies available in the case of parametrised strategies
    \item Extensible: easy to modify to include new strategies and to run new tournaments
\end{itemize}

\section*{Review of the literature}\label{sec:review}

@@

The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
for details) where two players repeatedly play the normal form game
of~(\ref{equ:one-shot}) in full knowledge of each other's playing history to
date.  An excellent description of the \textit{one shot} game is given
in~\cite{Gotts2003} which is paraphrased below:

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item If both choose \(C\), they receive a payoff of \(R\)
        (\textbf{R}eward);
    \item If both choose \(D\), they receive a payoff of \(P\)
        (\textbf{P}unishment);
    \item If one chooses \(C\) and the other \(D\), the defector receives a
        payoff of \(T\) (\textbf{T}emptation) and the cooperator a payoff of
        \(S\) (\textbf{S}ucker).
\end{itemize}

@@

The game of~(\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
although any satisfying the conditions in~\ref{equ:one-shot} will yield similar
results.  Axelrod's tournaments (and further implementations of these) are
sometimes referred to as Iterated Prisoner's Dilemma (IPD) tournaments. An
incomplete overview of published tournaments is given in
Table~\ref{tab:tournaments}.

@@

\section*{Implementation and architecture}

\section*{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software}
          (\url{http://gambit.sourceforge.net/})).
    \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
    \item Data manipulation \cite{mckinney-proc-scipy-2010}
          (\url{http://pandas.pydata.org/});
    \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
    \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
\end{itemize}

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\textwidth]{demo_tournament.pdf}
		\caption{The results from a simple tournament.}
		\label{fig:demo_tournament}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\textwidth]{stewart_tournament.pdf}
		\caption{The results from \cite{Stewart2012}.}
		\label{fig:stewart_tournament}
	\end{subfigure}
	\caption{Summary plots produced by the library.}
\end{figure}

@@

As stated in the \textbf{Introduction}, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

To date the library has had contributions from 24 contributors from a variety
of backgrounds. These contributions have been in terms of strategies. One
strategy is the creation of an undergraduate mathematics student with little
prior knowledge of programming. Multiple other strategies were written by a 15
year old secondary school student. Both of these students are authors of this
paper. As well as these strategy contributions, vital architectural
improvements to the library itself have also been received. You can see an
overview of the structure of the source code in Figure~\ref{fig:overview}.

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.75\textwidth]{outline_of_library.pdf}
		\caption{An overview of the source code.}
		\label{fig:overview}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\textwidth]{number_of_strategies_with_arima_projection.pdf}
		\caption{The number of strategies included in the library}
		\label{fig:number_of_strategies_against_date}
	\end{subfigure}
	\caption{An overview of the library.}
\end{figure}

\section*{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}

@@

\begin{multicols}{2}
    \begin{enumerate}[noitemsep,topsep=0pt]
        \item Cooperator
        \item Defector
        \item ZD-Extort-2
        \item Joss: 0.9
        \item Hard Tit For Tat
        \item Hard Tit For 2 Tats
        \item Tit For Tat
        \item Grudger
        \item Tit For 2 Tats
        \item Win-Stay Lose-Shift
        \item Random: 0.5
        \item ZD-GTFT-2
        \item GTFT: 0.33
        \item Hard Prober
        \item Prober
        \item Prober 2
        \item Prober 3
        \item Calculator
        \item Hard Go By Majority
    \end{enumerate}
\end{multicols}

@@

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()
    \end{minted}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.75\textwidth]{tournament.pdf}
	\caption{Results from the library tournament (2016-03-31)}
	\label{fig:tournament}
\end{figure}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item A closer look at zero determinant strategies, showing that
        extortionate strategies obtain a large number of wins \textit{but} do
        not perform particularly well. This is relevant given the findings of
        \cite{Stewart2012} in which zero determinant strategies are shown to be
        able to perform better than any other strategy. This finding extends
        to noisy tournaments (which are also implemented in the library).
    \item This negative relationship between wins and performance does not
        generalise. There are some strategies that perform well, both in terms
        of matches won and overall performance: Back stabber, Double crosser,
        Looker Up, and Fool Me Once. These strategies continue to perform well in noisy
        tournaments, however some of these have knowledge of the length of the
        game (Back stabber and Double crosser). This is not necessary to rank
        well in both wins and score as demonstrated by Looker Up and Fool Me
        Once.
    \item Strategies like Looker Up and Meta Hunter seem to be generally
        cooperative yet still exploit naive strategies. The MetaHunter strategy
        is a particular type of Meta strategy which uses a variety of other
        strategy behaviours to choose a best action. These strategies perform
        very well in general and continue to do so in noisy tournaments.
\end{itemize}

@@

\section*{(2) Availability}\label{sec:availability}

\section*{Operating system}

The Axelrod library runs on all major operating systems: Linux, Mac OSX and
Windows.

\section*{Programming language}

The library is continuously tested for Python 2.7, 3.3, 3.4 and 3.5.

\section*{Additional system requirements}

There are no specific additional system requirements.

\section*{Support}

Support is readily available in multiple forms:

\begin{itemize}[noitemsep,topsep=0pt]
    \item An online chat channel:
        \url{https://gitter.im/Axelrod-Python/Axelrod}.
    \item An  email group:
        \url{https://groups.google.com/forum/#!topic/axelrod-python}.
\end{itemize}

\section*{Dependencies}

The following Python libraries are required dependencies:

\begin{multicols}{3}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item Numpy 1.9.2:
        \item Matplotlib 1.4.2:
        \item Cloudpickle  0.1.1:
        \item Hypothesis  3.0:
        \item Testfixtures  4.9.1:
    \end{itemize}
\end{multicols}

\section*{List of contributors}

The names of all the contributors are not known: as these were mainly done
through Github and certain have not provided their name or responded to a
request for further details. Here is an incomplete list:

\begin{multicols}{2}
    \begin{itemize}[noitemsep,topsep=0pt]
        \item {Owen Campbell}
        \item {Mark Harper}
        \item {Vincent Knight}
        \item {Karol Langner}
        \item {James Campbell}
        \item {Thomas Campbell}
        \item {Alex Carney}
        \item {Martin Chorley}
        \item {Cameron Davidson-Pilon}
        \item {Kristian Glass}
        \item {Tom{\'a}{\v s} Ehrlich}
        \item {Martin Jones}
        \item {Georgios Koutsovoulos}
        \item {Marissa Tibble}
        \item {Jochen M{\"u}ller}
        \item {Geraint Palmer}
        \item {Paul Slavin}
        \item {Timothy Standen}
        \item {Luis Visintini}
        \item {Karl Molden}
        \item {Jason Young}
        \item {Andy Boot}
        \item {Anna Barriscale}
    \end{itemize}
\end{multicols}

\section*{Software location:}

{\bf Archive}

\begin{description}[noitemsep,topsep=0pt]
    \item[Name:] Zenodo
    \item[Persistent identifier:]
\href{https://zenodo.org/record/45187}{10.5281/zenodo.45187}
    \item[Licence:] MIT
    \item[Publisher:]  Vincent Knight
    \item[Version published:] Axelrod: Alternator Release. v0.0.28
    \item[Date published:] 2016-01-26
\end{description}

{\bf Code repository}

\begin{description}[noitemsep,topsep=0pt]
    \item[Name:] Github
    \item[Identifier:] \url{https://github.com/Axelrod-Python/Axelrod}
    \item[Licence:] MIT
    \item[Date published:] 2015-02-16
\end{description}

\section*{Reuse potential}\label{sec:reuse}

The Axelrod library has been designed with sustainable software practice in
mind. There is an extensive documentation suite:
\url{axelrod.readthedocs.org/en/latest/}. Furthermore, there is a growing set
of example Jupyter notebooks available here:
\url{https://github.com/Axelrod-Python/Axelrod-notebooks}.

The ability to have readily available a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theoretic community.
This has been evidenced by the work described: the library has already shown
it's potential for reuse.

\section*{Conclusion}

@@

\begin{itemize}[noitemsep,topsep=0pt]
    \item Noisy tournaments;
    \item Tournaments with probabilistic ending of interactions;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
\end{itemize}

@@

\section*{Acknowledgements}

The authors would like to thank all contributors. Also, they thank
Robert Axelrod himself for his well wishes with the library.

\section*{Competing interests}

The authors declare that they have no competing interests.

>>>>

\documentclass{article}

% Nicer bibliography management
\usepackage[backend=biber, backref=true, firstinits=true, url=true, isbn=true]{biblatex}
\addbibresource{references.bib}
%-----------------------------

% Lazy page formating (we can adjust when submitting)
\usepackage{fullpage}
\usepackage[parfill]{parskip}
%-----------------------------

\usepackage{amsmath}  % Basic
\usepackage{hyperref}  % Links etc
\usepackage{booktabs}  % Better tables
\usepackage{minted}  % Code
\usepackage{graphicx}  % Images
\usepackage{subcaption}  % Subfigures
\usepackage{authblk}  % Authors

\title{An open reproducible framework for the study of the iterated prisoner's
dilemma}

% Core devs (alphabetic order of last name)
\author[1]{Owen Campbell}
\author[1]{Mark Harper}
\author[2]{Vincent Knight}
\author[6]{Karol M. Langner}

% All devs (alphabetic order of last name)
\author[2]{James Campbell}
\author[5]{Thomas Campbell}
\author[2]{Alex Carney}
\author[2]{Martin Chorley}
\author[1]{Cameron Davidson-Pilon}
\author[1]{Kristian Glass}
\author[1]{Tom{\'a}{\v s} Ehrlich}
\author[1]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[1]{Holly Marissa}
\author[1]{Jochen M{\"u}ller}
\author[2]{Geraint Palmer}
\author[3]{Paul Slavin}
\author[2]{Timothy Standen}
\author[1]{Luis Visintini}
\author[1]{Karl ?}

% Affiliations
\affil[1]{Not affiliated}
\affil[2]{Cardiff University}
\affil[3]{The University of Manchester}
\affil[4]{The University of Edinburgh}
\affil[5]{St. Nicholas Catholic High School, Hartford}
\affil[6]{Google Inc., Mountain View, CA}

% Corresponding author

\date{\today}

\begin{document}

\maketitle
\begin{center}
    \thanks{Corresponding author: Vincent Knight
        \href{mailto:knightva@cf.ac.uk}{knightva@cf.ac.uk}}
\end{center}

\begin{abstract}
\noindent
    The Axelrod library is an open source Python package that allows for
    reproducible game theoretic research into the Iterated Prisoner's Dilemma.
    This area of research began in the 1980s but suffers from a lack of
    documentation and test code. The goal of the library is to provide such
    a resource, with facilities for the design of new strategies and
    interactions between them, as well as conducting tournaments and ecological
    simulations for populations of strategies.

\noindent
    With a growing collection of 120 strategies, the library is a also a
    platform for an original tournament that, in itself, is of interest to the
    game theoretic community.

\noindent
    This paper describes the Iterated Prisoner's Dilemma, the Axelrod library
    and its development, and insights gained from some novel research.
\end{abstract}

\section{Introduction}\label{sec:introduction}

@@

\begin{itemize}
    \item To enable the reproduction of Iterated Prisoner's Dilemma
    research as easily as possible
    \item To produce the de-facto tool for any future Iterated Prisoner's
    Dilemma research
    \item To provide as simple a means as possible for anyone to define and
    contribute new and original Iterated Prisoner's Dilemma strategies
\end{itemize}

@@

\begin{itemize}
    \item Open: all code is released under an MIT license;
    \item Reproducible and well-tested: at the time of writing there is an excellent level of
        integrated tests with 99.37\% coverage
    \item Well-documented: all features of the library are documented for ease of
        use and modification
    \item Extensive: 123 strategies are included, with infinitely-many
        strategies available in the case of parametrised strategies
    \item Extensible: easy to modify to include new strategies and to run new tournaments
\end{itemize}

Before describing the package in more detail in
Section~\ref{sec:description-of-axelrod-python}, an overview of some previous
Iterated Prisoner's Dilemma research will be given in
Section~\ref{sec:review}. Section~\ref{sec:new-strategies-and-implications} will
describe some early research and a conclusion is offered in
Section~\ref{sec:conclusion}.

\subsection{Review of the literature}\label{sec:review}

@@

The tournament is based on an iterated game (see~\cite{Maschler2013} or similar
for details) where two players repeatedly play the normal form game of
(\ref{equ:one-shot}) in full knowledge of each other's playing history to date.
An excellent description of the \textit{one shot} game is given
in~\cite{Gotts2003} which is paraphrased below:

@@

\begin{itemize}
    \item If both choose \(C\), they receive a payoff of \(R\)
        (\textbf{R}eward);
    \item If both choose \(D\), they receive a payoff of \(P\)
        (\textbf{P}unishment);
    \item If one chooses \(C\) and the other \(D\), the defector receives a
        payoff of \(T\) (\textbf{T}emptation) and the cooperator a payoff of
        \(S\) (\textbf{S}ucker).
\end{itemize}

@@

The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Specific
numerical values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature,
although any satisfying the conditions in \ref{equ:one-shot} will yield similar
results.  Axelrod's tournaments (and further implementations of these) are
sometimes referred to as Iterated Prisoner's Dilemma (IPD) tournaments. An
incomplete overview of published tournaments is given in
Table~\ref{tab:tournaments}.

@@

\subsection{Description of the Axelrod Python package}\label{sec:description-of-axelrod-python}

@@

\begin{itemize}
    \item Machine learning \cite{scikit-learn} (\url{http://scikit-learn.org/});
    \item Visualisation \cite{Hunter:2007} (\url{http://matplotlib.org/});
    \item Mathematics \cite{sage} (\url{http://www.sagemath.org/});
    \item Astrophysics \cite{astropy} (\url{http://www.astropy.org/});
    \item Data manipulation \cite{mckinney-proc-scipy-2010} (\url{http://pandas.pydata.org/});
    \item Algorithmic Game Theory \cite{Mckelvey06gambit:software} (\url{http://gambit.sourceforge.net/})).
\end{itemize}

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/demo_tournament.pdf}
		\caption{The results from a simple tournament.}
		\label{fig:demo_tournament}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/stewart_tournament.pdf}
		\caption{The results from \cite{Stewart2012}.}
		\label{fig:stewart_tournament}
	\end{subfigure}
	\caption{Summary plots produced by the library.}
\end{figure}

@@

As stated in Section~\ref{sec:introduction}, one of the main goals of the library
is to allow for the easy contribution of strategies. Doing this requires the
writing of a simple Python class (which can inherit from other predefined
classes). Full contribution guidelines can be found in the documentation.
As an example, Figures~\ref{fig:grudger} and~\ref{fig:grudger_test} show the source code for
the Grudger strategy as well as its corresponding test.

@@

To date the library has had contributions from 24 contributors from a variety of
backgrounds. These contributions have been in terms of strategies. One strategy
is the creation of an undergraduate mathematics student with little prior
knowledge of programming. Multiple other strategies were written by a 15 year old
secondary school student. As well as these strategy contributions, vital
architectural improvements to the library itself have also been received. You
can see an overview of the structure of the source code in
Figure~\ref{fig:overview}.

\begin{figure}[!hbtp]
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/outline_of_library.pdf}
		\caption{An overview of the source code.}
		\label{fig:overview}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=\textwidth]{../img/number_of_strategies_with_arima_projection.pdf}
		\caption{The number of strategies included in the library}
		\label{fig:number_of_strategies_against_date}
	\end{subfigure}
	\caption{An overview of the library.}
\end{figure}

Section~\ref{sec:new-strategies-and-implications} will describe in more detail
some of research capabilities of the library.

\section{New strategies, tournaments and implications}\label{sec:new-strategies-and-implications}

@@

\begin{enumerate}
    \item Cooperator
    \item Defector
    \item ZD-Extort-2
    \item Joss: 0.9
    \item Hard Tit For Tat
    \item Hard Tit For 2 Tats
    \item Tit For Tat
    \item Grudger
    \item Tit For 2 Tats
    \item Win-Stay Lose-Shift
    \item Random: 0.5
    \item ZD-GTFT-2
    \item GTFT: 0.33
    \item Hard Prober
    \item Prober
    \item Prober 2
    \item Prober 3
    \item Calculator
    \item Hard Go By Majority
\end{enumerate}

@@

>>> strategies = [axelrod.Cooperator(),
...               axelrod.Defector(),
...               axelrod.ZDExtort2(),
...               axelrod.Joss(),
...               axelrod.HardTitForTat(),
...               axelrod.HardTitFor2Tats(),
...               axelrod.TitForTat(),
...               axelrod.Grudger(),
...               axelrod.TitFor2Tats(),
...               axelrod.WinStayLoseShift(),
...               axelrod.Random(),
...               axelrod.ZDGTFT2(),
...               axelrod.GTFT(),
...               axelrod.HardProber(),
...               axelrod.Prober(),
...               axelrod.Prober2(),
...               axelrod.Prober3(),
...               axelrod.Calculator(),
...               axelrod.HardGoByMajority()]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{Source code for reproducing the tournament of \cite{Stewart2012}}
    \label{fig:stewart-code}
\end{figure}

@@

\begin{figure}[!hbtp]
	\centering
	\includegraphics[width=.9\textwidth]{../img/tournament.pdf}
	\caption{Results from the library tournament (2016-03-31)}
	\label{fig:tournament}
\end{figure}

@@

\begin{itemize}
    \item A closer look at zero determinant strategies, showing that
        extortionate strategies obtain a large number of wins \textit{but} do
        not perform particularly well. This is relevant given the findings of
        \cite{Stewart2012} in which zero determinant strategies are shown to be
        able to perform better than any other strategy. This finding extends
        to noisy tournaments (which are also implemented in the library).
    \item This negative relationship between wins and performance does not
        generalise. There are some strategies that perform well, both in terms
        of matches won and overall performance: Back stabber, Double crosser,
        Looker Up, and Fool Me Once. These strategies continue to perform well in noisy
        tournaments, however some of these have knowledge of the length of the
        game (Back stabber and Double crosser). This is not necessary to rank
        well in both wins and score as demonstrated by Looker Up and Fool Me
        Once.
    \item Strategies like Looker Up and Meta Hunter seem to be generally
        cooperative yet still exploit naive strategies. The MetaHunter strategy
        is a particular type of Meta strategy which uses a variety of other
        strategy behaviours to choose a best action. These strategies perform
        very well in general and continue to do so in noisy tournaments.
\end{itemize}

@@

\section{Conclusion}\label{sec:conclusion}

@@

\begin{itemize}
    \item Noisy tournaments;
    \item Tournaments with probabilistic ending of interactions;
    \item Ecological analysis of tournaments;
    \item Morality metrics based on \cite{Singer-Clark2014};
    \item Transformation of strategies (in effect giving an infinite number of
        strategies);
    \item Classification of strategies according to multiple dimensions.
    \item Gathering of full interaction history for all interactions.
\end{itemize}

@@

The ability to have readily available a large number of strategies makes this
tool an excellent and obvious example of the benefits of open research which
should positively impact the game theoretic community.
